Analysis Stand Features 

### 2017-05-09 analysis/analysis_stand_features.Rmd
add stand features

---
title: "Competence distance"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
```

# Read data 
```{r, echo=FALSE}
#machine <- 'ajpelu'
machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# density data 
compete <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')
```

```{r}
# Compute diameter normal (in meters)
compete <- compete %>% 
  mutate(dn = (perim_mm/1000) /pi) 
```

>>>>

---
title: "Analysis Stand Features "
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 May"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("raster")
library("stringr")
library('rgdal')
library("sp")
```

# Read and prepare data 
```{r, echo=FALSE}
machine <- 'ajpelu'
# machine <- 'ajpeluLap'
di <- paste0('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro/', sep='')

# Read tree data
tree <- read.csv(file=paste0(di, '/data_raw/dendro_competence.csv'), header=TRUE, sep=',')

# Read spatial data 
# Centroid of focal tree 
## filename 
mygpx_ca <- paste0(di, 'data_raw/geoinfo/dendro_ca.GPX')
mygpx_sj <- paste0(di, 'data_raw/geoinfo/dendro_sj.GPX')

## reading  
field_work_ca <- readOGR(mygpx_ca, layer="waypoints", verbose = FALSE)
field_work_sj <- readOGR(mygpx_sj, layer="waypoints", verbose = FALSE)
```

* Two datasets: focal tree and competence 
```{r}
# Compute diameter (mm)
tree <- tree %>% 
  mutate(dn_mm = (perim_mm / pi))

# Set levels of eleveation 
sj_lowcode  <- paste0('A', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('A', 11:20)
ca_lowcode <- c(paste0('B', str_pad(1:10, 2, pad='0')),
            paste0('B', 26:30))
ca_highcode <- paste0('B', 11:25)

tree <- tree %>% 
  mutate(elevF = ifelse(id_focal %in% sj_lowcode, 'Low',
                       ifelse(id_focal %in% sj_highcode, 'High',
                              ifelse(id_focal %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF))

# Get only focal trees  
ft <- tree %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno')

# Get only no focal trees 
nft <- tree %>% 
  filter(sp!='Focal') 
```

# Spatial Info
```{r, spatialData} 
## Get coordinates of spatial data  
sp_ca <- as.data.frame(field_work_ca) %>% 
  dplyr::select(ele, name, lat = coords.x2, long = coords.x1)

sp_sj <- as.data.frame(field_work_sj) %>% 
  dplyr::select(ele, name, lat = coords.x2, long = coords.x1)

## Add code site and get centroid (see # http://rspatial.org/analysis/rst/8-pointpat.html)
sp_ca <- sp_ca %>% 
  mutate(loc = 'CA', 
         elevF = ifelse(name %in% ca_lowcode, 'Low', 'High'),
         site = paste0(loc, '_', elevF))

coord_ca <- sp_ca %>% 
  group_by(site) %>%
  summarise(lat_m = mean(lat),
            long_m = mean(long))

# plot(sp_ca$long, sp_ca$lat, pch=19, col='gray')
# points(coord_ca$long_m, coord_ca$lat_m, pch=19, col='blue')

sp_sj <- sp_sj %>% 
  mutate(loc = 'SJ', 
         elevF = ifelse(name %in% sj_lowcode, 'Low', 'High'),
         site = paste0(loc, '_', elevF))        
coord_sj <- sp_sj %>% 
  group_by(site) %>%
  summarise(lat_m = mean(lat),
            long_m = mean(long))

coords_sites <- coord_sj %>% rbind(coord_ca)

#plot(sp_sj$long, sp_sj$lat, pch=19, col='gray')
#points(coord_sj$long_m, coord_sj$lat_m, pch=19, col='blue')

# Topographic data
```{r}
# Read topo data 
topo <- read.csv(file=paste(di, "/data/topo/topo.csv", sep=""), header=TRUE, sep=',')

topo <- topo %>% 
  mutate(loc = ifelse(str_detect(name, "A"), 'SJ', 'CA'),
         elevF = ifelse(name %in% sj_lowcode, 'Low',
                        ifelse(name %in% sj_highcode, 'High',
                              ifelse(name %in% ca_lowcode, 'Low', 'High')))) %>%
  mutate(site = paste0(loc, '_', elevF))

topo_summary <- topo %>%
  group_by(site) %>%
  summarise(mde_m = mean(mde),
            mde_sd = sd(mde),
            mde_min = min(mde),
            mde_max = max(mde),
            slope_m = mean(slope),
            slope_sd = sd(slope))
